Supplementary Material \\

### 2022-01-04 supplementary.tex
Updates from Overleaf

For random forest, gradient boost, and decision tree, we found that by adjusting most of the available parameters responded to severe overfitting. Therefore, most parameters are the default values defined by Scikit-learn. The only parameter that we found that could potentially improve the evaluation metric F$1$ was the maximum number of depth for the trees grown, which we adjusted between $1$ and $8$. For logistic regression, we chose to adjust the regularization strength with seven logarithmical adjusted values from $10^{-3}$ to $10^{5}$, and use either $200$ or $400$ iterations to reach convergence.

When searching for the optimal number of principal components, we iterated over every odd number of principal components from $1$ to the upper restricted number which defines an accumulated variance of $95\%$ from the principal component analysis. Due to a large number of principal components, we end up fitting $25$ folds for each of the $1232$ parameter combinations, totalling up to $30800$ individual models, just for logisitic regression for one approach.

%Ferrenti 
We visualize the grid search for the optimal number of principal components for the Ferrenti approach in figure \ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score on the test set as a function of principal components used in the models. For each principal component, the optimal combination of hyperparameters based on the F$1$-score is visualized.

In table \ref{tab:01-pc}, we find the precise measurements for each evaluation metrics for the optimal number of principal components, which is visualized as dotted lines in \ref{fig:01-pca}. The relevant hyperparameters for logistic regression were the maximum iterations, which was set at $400$, and the regularization term, which was found optimal at $0.46$. For random forest and decision trees, we find the maximum depth of $7$, while being $4$ for gradient boost. We find the best performing model is logistic regression, but is dependent on a large amount of principal components.

>>>>

For random forest, gradient boost, and decision tree, we found that by adjusting most of the available parameters responded to severe overfitting. Therefore, most parameters are the default values defined by Scikit-learn. The only parameter that we found that could potentially improve the evaluation metric F$1$ was the maximum number of depth for the trees grown, which we adjusted between $1$ and $8$. For logistic regression, we chose to adjust the regularization strength with seven logarithmic adjusted values from $10^{-3}$ to $10^{5}$, and use either $200$ or $400$ iterations to reach convergence.

When searching for the optimal number of principal components, we iterated over every odd number of principal components from $1$ to the upper restricted number which defines an accumulated variance of $95 \ \%$ from the principal component analysis. Due to a large number of principal components, we end up fitting $25$ folds for each of the $1232$ parameter combinations, totaling up to $30.800$ individual models, just for logistic regression for one approach.

%Ferrenti 
We visualize the grid search for the optimal number of principal components for the Ferrenti approach in Figure~\ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score on the test set as a function of principal components used in the models. For each principal component, the optimal combination of hyperparameters based on the F$1$-score is visualized.

In Table~\ref{tab:01-pc}, we find the precise measurements for each of the evaluation metrics for the optimal number of principal components, which is visualized as dotted lines in Fig.~\ref{fig:01-pca}. The relevant hyperparameters for logistic regression were the maximum iterations, which was set at $400$, and the regularization term, which was found optimal at $0.46$. For random forest and decision trees, we find the maximum depth of $7$, while being $4$ for gradient boost. We find the best performing model is logistic regression, but is dependent on a large amount of principal components.
